### 2019-01-08 Sections/protocols_for_the_quantum_internet.tex
minor

To implement this protocol, rather than first distributing a Bell pair between sender and recipient, we distribute an $n$-party GHZ state between the sender and the \mbox{$n-1$} recipients,
\begin{align}
\ket{\psi_\mathrm{GHZ}^{(n)}} = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}).
\end{align}

@@

The full protocol is described in Alg.~\ref{alg:open_dest_qst}, and outlined in Fig.~\ref{fig:open_dest_teleport}. This protocol was successfully experimentally demonstrated photonically using 5 qubits \cite{bib:PanOpenDest}, with high teleported state fidelities.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{open_dest_teleport_long}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{open_dest_teleport}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure*}
\fi

>>>>

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{open_dest_teleport_long}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation, resulting in the state being teleported to all recipients in redundantly-encoded\index{Redundant encoding} form. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of just the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{open_dest_teleport}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation, resulting in the state being teleported to all recipients in redundantly-encoded\index{Redundant encoding} form. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of just the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure*}
\fi

To implement this protocol, outlined in Fig.~\ref{fig:open_dest_teleport}, rather than first distributing a Bell pair between sender and recipient, we distribute an $n$-party GHZ state between the sender and the \mbox{$n-1$} recipients,
\begin{align}
\ket{\psi_\mathrm{GHZ}^{(n)}} = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}).
\end{align}

@@

The full protocol is described in Alg.~\ref{alg:open_dest_qst}. This protocol was successfully experimentally demonstrated photonically using 5 qubits \cite{bib:PanOpenDest}, with high teleported state fidelities.

@@
